\documentclass[a4paper,10pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
% \usepackage{parskip}
\setlength{\parskip}{0pt} 
\usepackage{microtype}
\usepackage{multicol}

% --- Compact layout ---
\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{0.6em}{0.35em}

\setlist[itemize]{leftmargin=*,topsep=1pt,partopsep=0pt,parsep=0pt,itemsep=0pt}
\setlist[enumerate]{leftmargin=*,topsep=1pt,partopsep=0pt,parsep=0pt,itemsep=0pt}

\pagestyle{empty}

\begin{document}

%-------------------- Header --------------------%
\begin{center}
    {\Huge \textbf{Lei Zhang}}\\
    Postdoctoral Researcher, Ruhr University Bochum (ICAMS)\\
    \textbf{Website:} \href{https://leizhanglab.com}{\underline{leizhanglab.com}} \\
    \textbf{Email:} \href{mailto:Lei.Zhang-w2i@ruhr-uni-bochum.de}{Lei.Zhang-w2i@ruhr-uni-bochum.de} \\
    \textbf{ORCID:} \href{https://orcid.org/0009-0003-5842-1932}{\underline{link}} \quad
    \textbf{Google Scholar:} \href{https://scholar.google.com/citations?user=G-WvdhIAAAAJ}{\underline{link}} \quad
    \textbf{ResearchGate:} \href{https://www.researchgate.net/profile/Lei-Zhang-871}{\underline{link}}
\end{center}

%-------------------- Summary --------------------%
\section*{Summary}
Postdoctoral researcher applying NLP and machine learning for data-driven electrocatalyst discovery. Creator of \textsc{MatNexus}, an open-source framework for automated literature collection, text mining, and embedding-based property prediction. Current work integrates NLP, multi-modal learning, and optimisation with experimental validation.

%-------------------- Education --------------------%
\section*{Education}
\textbf{PhD in Materials Science} \hfill 2022--2025\\
Ruhr University Bochum (ICAMS), Germany\\
Thesis: \textit{Accelerating Materials Discovery through Text Mining and Machine Learning: A Data-Driven Approach}\\
Supervisor: Prof. Markus Stricker (\href{https://www.icams.de/institute/icams/members/members-detail/?detail=1889}{\underline{link}})\\

\textbf{Master’s Degree in Materials Science} \hfill 2019--2022\\
NanChang Hangkong University, China\\
Thesis: \textit{Electrocatalyst Design and Preparation: A Laboratory-Based Approach}\\[2pt]

\textbf{Bachelor’s Degree in Welding Technology} \hfill 2013--2017\\
NanChang Hangkong University, China

%-------------------- Research Experience --------------------%
\section*{Research Experience}

\textbf{Postdoctoral Researcher}, Ruhr University Bochum (ICAMS) \hfill 2025--Present
\begin{itemize}
    \item Extending \textsc{MatNexus} with advanced NLP, multi-modal learning, and optimisation for materials discovery.
    \item Leading collaborations with experimental groups (incl. Prof. Alfred Ludwig’s team: \href{https://www.mdi.ruhr-uni-bochum.de/mdi/mitarbeiter/ludwig.html.en}{\underline{link}}) to prioritise candidate compositions and validate predictions.
    \item Contributing to CRC 1625 (\href{https://www.ruhr-uni-bochum.de/crc1625/}{\underline{link}}), DIMENSION (\href{https://mercur-research.de/projekte/default-466034e9780fc5fbe19391cd2911c3a5/dimension}{\underline{link}}), and COST CA22154 (\href{https://www.cost.eu/}{\underline{link}}).
\end{itemize}

\textbf{PhD Researcher}, Ruhr University Bochum (ICAMS) \hfill 2022--2025
\begin{itemize}
    \item Developed \textsc{MatNexus}: automated literature mining + word-embedding pipelines for materials discovery.
    \item Built Python workflows for data curation, NLP, model training/evaluation; supported composition--property prediction.
    \item Collaborated with experimental partners for synthesis guidance and validation.
\end{itemize}

\textbf{Master’s Researcher}, NanChang Hangkong University \hfill 2019--2022
\begin{itemize}
    \item Experimental electrocatalyst development (molten-salt synthesis, scale-up, electrochemical evaluation)
\end{itemize}

%-------------------- Publications --------------------%
\section*{Publications}

\textbf{PhD / Current Research}

\textit{Peer-reviewed}
\begin{enumerate}
    \item \textbf{Zhang, L.} and Stricker, M. \textit{MatNexus: A comprehensive text mining and analysis suite for materials discovery}. \textit{SoftwareX} 26 (2024). DOI: \href{https://doi.org/10.1016/j.softx.2024.101654}{10.1016/j.softx.2024.101654}
    \item \textbf{Zhang, L.}, Banko, L., Schuhmann, W., Ludwig, A., Stricker, M. \textit{Composition-property extrapolation for compositionally complex solid solutions based on word embeddings}. \textit{Digital Discovery} (2025). DOI: \href{https://doi.org/10.1039/D5DD00169B}{10.1039/D5DD00169B}
    \item \textbf{Zhang, L.} and Stricker, M. \textit{Iterative Corpus Refinement for Materials Property Prediction Based on Scientific Texts}. ECML PKDD (2025). DOI: 10.1007/978-3-032-06118-8\_6
    \item Stricker, M., Banko, L., Sarazin, N., Siemer, N., Janssen, J., \textbf{Zhang, L.}, Neugebauer, J., Ludwig, A. \textit{Computationally accelerated experimental materials characterization}. \textit{Nature Communications} (2026). DOI: 10.1038/s41524-025-01919-5.
\end{enumerate}

\textit{Preprints}
\begin{enumerate}
    \item \textbf{Zhang, L.} and Stricker, M. \textit{Electrocatalyst discovery through text mining and multi-objective optimization}. arXiv (2025). \href{https://arxiv.org/abs/2502.20860}{arXiv:2502.20860}
\end{enumerate}

\textbf{Master’s Research}

\textit{Peer-reviewed}

\begin{enumerate}
    \item Hu, Z., Chen, Z., Huang, J., Yan, M., Zhang, M., \textbf{Zhang, L.}, Li, X., Feng, Z. \textit{Graphene-based SiC nanowires with nanosheets}. \textit{CrystEngComm} 22(24) (2020) 4074--4078. DOI: \href{https://doi.org/10.1039/d0ce00297f}{10.1039/d0ce00297f}
    \item Hu, Z., \textbf{Zhang, L.}, Huang, J., et al. \textit{Self-supported Ni-doped Mo\textsubscript{2}C nanoflowers on CFP for HER}. \textit{Nanoscale} 13(17) (2021) 8264--8274. DOI: \href{https://doi.org/10.1039/d1nr00169h}{10.1039/d1nr00169h}
    \item Yan, M., Xiong, Q., Huang, J., \textbf{Zhang, L.}, et al. \textit{Molten salt synthesis of TiC using carbon templates}. \textit{Ceramics International} 47(12) (2021) 17589--17596. DOI: \href{https://doi.org/10.1016/j.ceramint.2021.03.077}{10.1016/j.ceramint.2021.03.077}
    \item \textbf{Zhang, L.}, Huang, J., Hu, Z., et al. \textit{Ni-doped Mo\textsubscript{2}C@CFP electrode via molten salt for HER}. \textit{Rare Metal Materials and Engineering} 51(4) (2022) 1341--1347.
    \item \textbf{Zhang, L.}, Huang, J., Li, X., et al. \textit{Ni(NO\textsubscript{3})\textsubscript{2}-induced WC coating on CFP for HER via molten salt}. \textit{Electrochimica Acta} 422 (2022) 140553. DOI: \href{https://doi.org/10.1016/j.electacta.2022.140553}{10.1016/j.electacta.2022.140553}
    \item \textbf{Zhang, L.}, Hu, Z., Huang, J., et al. \textit{Experimental and DFT studies of Ni-doped Mo\textsubscript{2}C on CFP for HER}. \textit{Journal of Advanced Ceramics} 11(8) (2022) 1294--1306. DOI: \href{https://doi.org/10.1007/s40145-022-0610-6}{10.1007/s40145-022-0610-6}
    \item Luo, Z., \textbf{Zhang, L.}, Huang, J., et al. \textit{Ni-doped WC/Mo\textsubscript{2}C on CFP via molten salt for HER}. \textit{Ceramics International} 49(11A) (2023) 17993--17999. DOI: \href{https://doi.org/10.1016/j.ceramint.2023.02.073}{10.1016/j.ceramint.2023.02.073}
    \item Ding, T., \textbf{Zhang, L.}, Huang, J., et al. \textit{P-Ni co-doped Mo\textsubscript{2}C embedded in carbon-fiber paper for alkaline HER}. \textit{Diamond and Related Materials} 143 (2024) 110942. DOI: \href{https://doi.org/10.1016/j.diamond.2024.110942}{10.1016/j.diamond.2024.110942}
\end{enumerate}

\textit{Patents}
\begin{itemize}
    \item CN113072069A; CN113073351A; CN110368969A.
\end{itemize}

%-------------------- Conference Presentations --------------------%
\section*{Conference Presentations}

\begin{itemize}
    \item 2025 -- AIMSE2025 (Bochum, Germany): ``Literature-Based Prediction of High-Performance Electrocatalysts.''
    \item 2025 -- ECML PKDD (Porto, Portugal): ``Iterative Corpus Refinement for Materials Property Prediction Based on Scientific Texts.''
    \item 2024 -- MLM4MS (Ljubljana, Slovenia): ``Prediction of quaternary systems based on word embeddings.''
    \item 2024 -- MMM11 (Prague, Czech Republic): ``Vector analysis for improved prediction of quaternary material systems.''
    \item 2024 -- Early Career Researchers Day, RUB (Bochum, Germany): ``MatNexus: text mining suite for materials discovery.''
    \item 2023 -- FEMS EUROMAT (Frankfurt, Germany): ``From text data to word embeddings in Materials Science.''
    \item 2023 -- GC-MAC Summer School (KIT Karlsruhe, Germany): ``MatNexus: systematic text extraction in materials science.''
    \item 2022 -- WE-Heraeus-Seminar (Bad Honnef, Germany): ``From text data to word embeddings in Materials Science.''
\end{itemize}

% %-------------------- Skills --------------------%
% \section*{Skills}

% \begin{multicols}{2}
% \begin{itemize}
%     \item \textbf{Programming:} Python (NumPy, pandas, scikit-learn)
%     \item \textbf{NLP:} text mining, Word2Vec, spaCy, Gensim
%     \item \textbf{ML:} GPR, regression, clustering, evaluation
%     \item \textbf{Tools:} Git, Jupyter, LaTeX
%     \item \textbf{Data:} stats, visualisation (Matplotlib/Seaborn), large datasets
%     \item \textbf{Experimental:} molten-salt synthesis; electrochemical testing
%     \item \textbf{Collaboration:} interdisciplinary projects; mentoring
%     \item \textbf{Communication:} scientific writing; talks/outreach
% \end{itemize}
% \end{multicols}
% \clearpage
%-------------------- Fellowships, Awards, and Grants --------------------%
\section*{Fellowships, Awards, and Grants}

\begin{multicols}{2}
\begin{itemize}
    \item Research Fellowship, RUB \hfill 2025
    \item Doctorate with Distinction \hfill 2025
    \item CSC Scholarship \hfill 2022--2025
    \item First Place, Science Slam (RUB) \hfill 2024
    \item Excellent Graduate Student \hfill 2022
    \item Jiangxi Gov.\ Scholarship \hfill 2021
    \item First Class Postgraduate Scholarship \hfill 2019--2022
    \item Microstructure Photography (1st Prize) \hfill 2020
    \item Postgraduate Forum (1st Prize) \hfill 2020
    \item National Scholarship \hfill 2017
    \item NCHU Scholarship \hfill 2013--2017
\end{itemize}
\end{multicols}

%-------------------- Teaching Experience --------------------%
\section*{Teaching Experience}
\begin{itemize}
    \item Mentor, course project (2024): \textit{Comparative Analysis of Descriptors in Electrocatalysis}.
    \item Supervisor, student assistant (2024): data collection/analysis and text-mining workflows for materials discovery.
\end{itemize}

\end{document}
